---
title: "Final Rmarkdown Portfolio"
author: "Elise Johnson"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# ABSTRACT



# BACKGROUND


# STUDY QUESTION and HYPOTHESIS

## Questions  
Is there a correlation between the proportion of low air quality days and prevalence of asthma per state? 

## Hypothesis 
Where you live has an effect on whether you experience asthma or not
  
## Prediction
I predict that the state you live in does impact your chances of having asthma. The states with lower air quality will have higher rates of asthma. 


# METHODS


## First analysis
```{r plot1, eval=TRUE}
# code for figure 1
mydata<- read.csv("groupfile.csv")
# library
library(ggplot2)
 
# The iris dataset is provided natively by R
#head(iris)
 
# basic scatterplot
ggplot(mydata, aes(x=Proportion.of..poor.air.quality..days, y=Percent.Adults.with.Current.Asthma)) + 
    geom_point()
```

## Second analysis/plot
```{r plot2, eval=FALSE}


# DISCUSSION

## Interpretation 1 -



## Interpretation 2 -


# CONCLUSION

# REFERENCES     

